---
title: 'E-field USC-MUSC dataset - TMS sims'
author: "Diego Arias"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(plyr)
library(dplyr)
library(tidyverse)
library(easystats)
library(ggpubr)
library(ggthemes)
library(Rmisc)
library(readr)
library(lme4)
library(nlme)
library(modelbased)
library(performance)
library(investr) 
library(raincloudplots) # remotes::install_github('jorvlan/raincloudplots')
library(ggstatsplot)
library(paletteer)
library(gtsummary)
library(smplot2)
library(emmeans)
library(ggplot2)


library(rstatix)
library(afex)
library(tidyverse)
library(ggdist)
library(ggthemes)
library(gridExtra)
library(report)

library(minpack.lm) # nlsLM function
library(zoo)

theme_set(theme_classic())

dir <- '/Users/ariasd/Library/CloudStorage/OneDrive-MedicalUniversityofSouthCarolina/Documents/GitHub/StrokeEfield_USC/data_matrices/healthy/TMS/anon'
dir_ex <- '/Users/ariasd/Library/CloudStorage/OneDrive-MedicalUniversityofSouthCarolina/Documents/GitHub/StrokeEfield_USC/data_matrices/excluded/adj'

#grp_age <-c('OLD','YNG','YNG','OLD','YNG',
#            'YNG','OLD','OLD','YNG','YNG',
#            'YNG','YNG','OLD','OLD','YNG',
#            'YNG','OLD','OLD','OLD','OLD',
#            'OLD','OLD','OLD','YNG','OLD',
#            'YNG','YNG','YNG','YNG','OLD',
#            'OLD')


# 5- Load e-fields magnitudes for T1+T2

fullpath <- file.path(dir, 'charm_T1_T2_qform_anon_adj_Emagn.csv')
#fullpath_ex <- file.path(dir_ex, 'charm_T1_T2_csf_noneck_sform_adj_Emagn.csv')

t1_t2.df <- read.csv(fullpath)
t1_t2.df$method <- 't1_t2'
t1_t2.df$modality <- 't1+t2'
t1_t2.df$FS <- 'off'
t1_t2.df$grp_age <- c('OLD','YNG','YNG','OLD','YNG',
            'YNG','OLD','OLD','YNG','YNG',
            'YNG','YNG','OLD','OLD','YNG',
            'YNG','OLD','OLD','OLD','OLD',
            'OLD','OLD','OLD','YNG','OLD',
            'YNG','YNG','YNG','YNG','OLD',
            'OLD')

t1_t2.df$age <- c(76, 39, 27, 65, 18,
            27, 63, 63, 22, 23,
            26, 30, 75, 65, 32,
            27, 63, 63, 61, 74,
            60, 73, 60, 23, 60,
            26, 27, 31, 22, 64,
            66)

#dataset = {'MMD_021','MMD_022', 'MMD_023', 'MMD_024', 'MMD_025', 
#  'MMD_026','MMD_027', 'MMD_028', 'MMD_030', 'MMD_031', 
#  'MMD_032','MMD_033', 'MMD_034', 'MMD_035', 'MMD_036', 
#  'MMD_037','MMD_038', 'MMD_039', 'MMD_041', 'MMD_043', 
#  'MMD_044','MMD_045', 'MMD_046', 'MMD_048', 'MMD_049', 
#  'MMD_050','MMD_052', 'MMD_053', 'MMD_054', 'MMD_055', 
#  'MMD_056'};


#ager <-c()
#t1_t2.df$seq_q <- c("Good", "Good", "Good", "Good", "Good",
#                    "Good", "Good", "Good", "Good", "Good",
#                    "Good", "Good", "Poor", "Good", "Good",
#                    "Poor", "Good", "Good", "Good", "Good",
#                    "Poor", "Good", "Good")

#t1_t2_ex.df <- read.csv(fullpath_ex)
#t1_t2_ex.df$method <- 't1_t2'
#t1_t2_ex.df$modality <- 't1+t2'
#t1_t2_ex.df$FS <- 'off'
#t1_t2_ex.df$LE <- 'off'
#t1_t2_ex.df$seq_q <- c("Good", "Good", "Good", "Good")


# 7- load e-fields magnitudes for T1+T2+Freesurfer

fullpath <- file.path(dir, 'charm_T1_T2_qform_fs_anon_adj_Emagn.csv')
#fullpath_ex <- file.path(dir_ex, 'charm_T1_T2_csf_noneck_sform_fs_adj_Emagn.csv')

t1_t2_fs.df <- read.csv(fullpath)
t1_t2_fs.df$method <- 't1_t2_fs'
t1_t2_fs.df$modality <- 't1+t2'
t1_t2_fs.df$FS <- 'on'
t1_t2_fs.df$grp_age <- c('OLD','YNG','YNG','OLD','YNG',
            'YNG','OLD','OLD','YNG','YNG',
            'YNG','YNG','OLD','OLD','YNG',
            'YNG','OLD','OLD','OLD','OLD',
            'OLD','OLD','OLD','YNG','OLD',
            'YNG','YNG','YNG','YNG','OLD',
            'OLD')

t1_t2_fs.df$age <- c(76, 39, 27, 65, 18,
            27, 63, 63, 22, 23,
            26, 30, 75, 65, 32,
            27, 63, 63, 61, 74,
            60, 73, 60, 23, 60,
            26, 27, 31, 22, 64,
            66)

#t1_t2_fs.df$seq_q <- c("Good", "Good", "Good", "Good", "Good",
#                       "Good", "Good", "Good", "Good", "Good",
#                       "Good", "Good", "Good", "Good", "Good",
#                       "Good", "Good", "Good", "Good", "Good",
#                       "Good", "Good","Good")

#t1_t2_fs_ex.df <- read.csv(fullpath_ex)
#t1_t2_fs_ex.df$method <- 't1_t2_fs'
#t1_t2_fs_ex.df$modality <- 't1+t2'
#t1_t2_fs_ex.df$FS <- 'on'
#t1_t2_fs_ex.df$LE <- 'off'
#t1_t2_fs_ex.df$seq_q <- c("Good", "Good", "Good", "Good")

# 8- load e-fields magnitudes for T1+T2+Freesurfer+le


# #t1_t2_fs_le.df$seq_q <- c("Good", "Good", "Good", "Good", "Good",
# #                       "Good", "Good", "Good", "Good", "Good",
# #                       "Good", "Good", "Good", "Good", "Good",
# #                       "Good", "Good", "Good", "Good", "Good",
# #                       "Good", "Good","Good")
#
#
# #t1_t2_fs_le_ex.df <- read.csv(fullpath_ex)
# #t1_t2_fs_le_ex.df$method <- 't1_t2_fs_le'
# #t1_t2_fs_le_ex.df$modality <- 't1+t2'
# #t1_t2_fs_le_ex.df$FS <- 'on'
# #t1_t2_fs_le_ex.df$LE <- 'on'
# #t1_t2_fs_le_ex.df$seq_q <- c("Good", "Good", "Good", "Good")
#
# #data_ex.df <- bind_rows(t1_ex.df, t1_fs_ex.df, t1_le_ex.df, t1_fs_le_ex.df,
# #                     t1_t2_ex.df, t1_t2_fs_ex.df, t1_t2_le_ex.df, t1_t2_fs_le_ex.df)


data.df <- bind_rows(t1_t2.df, t1_t2_fs.df)

#data.df <- bind_rows(t1.df, t1_fs.df, t1_le.df, t1_fs_le.df)

data_all.df <- data.df
#data.df <- bind_rows(t1.df, t1_fs.df, t1_le.df, t1_fs_le.df,  
#                     t1_t2.df, t1_t2_fs.df, t1_t2_le.df, t1_t2_fs_le.df)

#data.df <- data.df %>%
#  mutate(avg_E_magn = as.numeric(avg_E_magn),
#         avg_E_normal = as.numeric(avg_E_normal),
#         avg_E_tanget = as.numeric(avg_E_tanget),
##         n_nodes_roi = as.numeric(n_nodes_roi),
#         n_nodes_surf = as.numeric(n_nodes_surf))

#str(data.df)

sub_data_excl.df <- data.df #%>%
sub_data_all.df <- data_all.df
  #filter(subID != '216' & subID != '195' & subID != '218' & subID != '125')  
#filter(subID != '142' &  subID != '168' & subID != '188' & subID != '209' & subID != '213'  & subID != '222' )

#sub_data_wide <- sub_data_excl.df %>%
#   pivot_wider(
#     names_from = method,       # Column with categories to become new columns
#     values_from = c(avg_roi_E_magn, avg_roi_E_normal, avg_roi_E_tangent)      # Column with values to populate these columns
     
#   )

# define factors

#sub_data_excl.df$modality <-factor(sub_data_excl.df$modality)
#sub_data_excl.df$FS <-factor(sub_data_excl.df$FS)
#sub_data_excl.df$LE <-factor(sub_data_excl.df$LE)

sub_data_all.df$modality <-factor(sub_data_all.df$modality)
sub_data_all.df$FS <-factor(sub_data_all.df$FS)
sub_data_all.df$grp_age <-factor(sub_data_all.df$grp_age)


```

# Inspect raw data (basic box plots)

 T1+T2 vs T1+T2 + Freesurfer, separated by age (YNG, and OLD)

\*Freesurfer was generated based on T1 and T2.

## E-field magnitude


```{r}
ggplot(sub_data_all.df, aes(x = grp_age, y = avg_roi_E_magn, fill = FS)) +
  geom_boxplot(
    position = position_dodge(width = 0.7),
    color = "black",
    outlier.shape = NA,
    alpha = 0.5,
    width = 0.6
  ) +
  labs(
    x = "Age Group",
    y = "Average ROI E-field Magnitude",
    fill = "FreeSurfer"
  ) +
  theme_classic()
```

## Peak e-field

```{r}

ggplot(sub_data_all.df, aes(x = grp_age, y = p99_9, fill = FS)) +
  geom_boxplot(
    position = position_dodge(width = 0.7),
    color = "black",
    outlier.shape = NA,
    alpha = 0.5,
    width = 0.6
  ) +
  labs(
    x = "Age Group",
    y = "Average ROI E-field Magnitude",
    fill = "FreeSurfer"
  ) +
  theme_classic()

```

## normal component

```{r}


ggplot(sub_data_all.df, aes(x = grp_age, y = avg_roi_E_normal, fill = FS)) +
  geom_boxplot(
    position = position_dodge(width = 0.7),
    color = "black",
    outlier.shape = NA,
    alpha = 0.5,
    width = 0.6
  ) +
  labs(
    x = "Age Group",
    y = "Average ROI E-field Magnitude",
    fill = "FreeSurfer"
  ) +
  theme_classic()


```

because e-field estimates are very small when using a di/dt=1 A/us, the output need to be re scaled. TMS simulations considered the use of the cool-B65 AP coil

```{r}
scale_factor = 1.2*(150/2) # di/dt at MSO for cool-B65 AP coil
sub_data_all.df$avg_roi_E_magn_sc <- sub_data_all.df$avg_roi_E_magn*scale_factor
sub_data_all.df$avg_roi_E_normal_sc <- sub_data_all.df$avg_roi_E_normal*scale_factor
sub_data_all.df$p99_9_sc <- sub_data_all.df$p99_9*scale_factor

sub_data_all.df$age_c <-scale(sub_data_all.df$age,
                              center = TRUE,
                              scale = FALSE)

# also we substract the average from the age for interpretability of the model.




# because 
```

# plot scale data


```{r}

ggplot(sub_data_all.df, aes(x = grp_age, y = avg_roi_E_magn_sc, fill = FS)) +
  geom_boxplot(
    position = position_dodge(width = 0.7),
    color = "black",
    outlier.shape = NA,
    alpha = 0.5,
    width = 0.6
  ) +
  labs(
    x = "Age Group",
    y = "Average ROI E-field Magnitude",
    fill = "FreeSurfer"
  ) +
  theme_classic()


```

## Violin plot for manuscript: E-field magnitude

```{r}

# Optional: precompute means per combination
means_df <- sub_data_all.df %>%
  dplyr::group_by(grp_age, FS) %>%
  dplyr::summarise(mean_E = mean(avg_roi_E_magn_sc, na.rm = TRUE), .groups = "drop_last")

LE_labels <- c(
  "t1" = "T1",
  "t1+t2" = "T1 + T2"
)

ggplot(sub_data_all.df,
       aes(x = grp_age,
           y = avg_roi_E_magn_sc,
           fill = FS,
           color = FS)) +

  geom_violin(position = position_dodge(width = 0.7),
              alpha = 0.2,
              width = 0.7) +

  geom_jitter(position = position_jitterdodge(jitter.width = 0.15,
                                              dodge.width = 0.7),
              size = 1.5,
              alpha = 0.8) +

  geom_point(data = means_df,
             aes(x = grp_age, y = mean_E, fill = FS),
             shape = 23,
             size = 2.8,
             color = "black",
             position = position_dodge(width = 0.7)) +

  facet_wrap(~ modality, labeller = labeller(modality = LE_labels)) +
  scale_x_discrete(labels = c(
  "on" = "LE yes",
  "off" = "LE no"
)) +
  
   scale_fill_manual(
    values = c("on"  = "#FF7F0E",
               "off" = "#1F77B4"),  # orange
    name = "FS",
    labels = c("on" = "yes",
               "off"  = "no")
  ) +

  scale_color_manual(
    values = c("off" = "#1F77B4",
               "on"  = "#FF7F0E")
  ) +
   # scale_fill_discrete(
  #  name = "FS",
 #   labels = c("off" = "Off", "on" = "On")
 # ) +
#scale_y_continuous(limits = c(-0.05, 0.18))+
  labs(x = "",
       y = "Avg. E-field Magnitude (V/m)",
       fill = "Freesurfer") +
  
  guides(color = "none") +   # remove duplicate legend

  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        strip.text = element_text(size = 11, face = "bold"),
        strip.background = element_blank(),
        #legend.position = c(0.98, 0.98),
        legend.position = 'none',
        legend.direction = "horizontal",
        legend.justification = c(1, 1),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 10))


# Save figure
ggsave("violin_emagn_tms_healthy_anon.png",
       dpi = 300,
       width = 3.5,
       height = 4,
       units = "in")

```

## Violing plot for manuscript: normal component

```{r}

# Optional: precompute means per combination
means_df <- sub_data_all.df %>%
  dplyr::group_by(grp_age, FS) %>%
  dplyr::summarise(mean_E = mean(avg_roi_E_normal_sc, na.rm = TRUE), .groups = "drop_last")

LE_labels <- c(
  "t1" = "T1",
  "t1+t2" = "T1 + T2"
)

ggplot(sub_data_all.df,
       aes(x = grp_age,
           y = avg_roi_E_normal_sc,
           fill = FS,
           color = FS)) +

  geom_violin(position = position_dodge(width = 0.7),
              alpha = 0.2,
              width = 0.7) +

  geom_jitter(position = position_jitterdodge(jitter.width = 0.15,
                                              dodge.width = 0.7),
              size = 1.5,
              alpha = 0.8) +

  geom_point(data = means_df,
             aes(x = grp_age, y = mean_E, fill = FS),
             shape = 23,
             size = 2.8,
             color = "black",
             position = position_dodge(width = 0.7)) +

  facet_wrap(~ modality, labeller = labeller(modality = LE_labels)) +
  scale_x_discrete(labels = c(
  "on" = "LE On",
  "off" = "LE Off"
)) +
     scale_fill_manual(
    values = c("off" = "#1F77B4",   # blue
               "on"  = "#FF7F0E"),  # orange
    name = "FS",
    labels = c("off" = "Off",
               "on"  = "On")
  ) +

  scale_color_manual(
    values = c("off" = "#1F77B4",
               "on"  = "#FF7F0E")
  ) +
  #  scale_fill_discrete(
 #   name = "FS",
 #   labels = c("off" = "Off", "on" = "On")
#  ) +
#scale_y_continuous(limits = c(-0.05, 0.18))+
  labs(x = "",
       y = "Normal component (V/m)",
       fill = "Freesurfer") +
  
  guides(color = "none") +   # remove duplicate legend

  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        strip.text = element_text(size = 11, face = "bold"),
        strip.background = element_blank(),
        #legend.position = c(0.98, 0.98),
        legend.position = 'none',
        legend.direction = "horizontal",
        legend.justification = c(1, 1),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 10))


# Save figure
ggsave("violin_normal_tms_healthy_anon.png",
       dpi = 300,
       width = 3.5,
       height = 4,
       units = "in")

```


```{r}

# Optional: precompute means per combination
means_df <- sub_data_all.df %>%
  dplyr::group_by(grp_age, FS) %>%
  dplyr::summarise(mean_E = mean(p99_9_sc, na.rm = TRUE), .groups = "drop_last")

LE_labels <- c(
  "t1" = "T1",
  "t1+t2" = "T1 + T2"
)

ggplot(sub_data_all.df,
       aes(x = grp_age,
           y = p99_9_sc,
           fill = FS,
           color = FS)) +

  geom_violin(position = position_dodge(width = 0.7),
              alpha = 0.2,
              width = 0.7) +

  geom_jitter(position = position_jitterdodge(jitter.width = 0.15,
                                              dodge.width = 0.7),
              size = 1.5,
              alpha = 0.8) +

  geom_point(data = means_df,
             aes(x = grp_age, y = mean_E, fill = FS),
             shape = 23,
             size = 2.8,
             color = "black",
             position = position_dodge(width = 0.7)) +

  facet_wrap(~ modality, labeller = labeller(modality = LE_labels)) +
  scale_x_discrete(labels = c(
  "on" = "LE On",
  "off" = "LE Off"
)) +
     scale_fill_manual(
    values = c("off" = "#1F77B4",   # blue
               "on"  = "#FF7F0E"),  # orange
    name = "FS",
    labels = c("off" = "Off",
               "on"  = "On")
  ) +

  scale_color_manual(
    values = c("off" = "#1F77B4",
               "on"  = "#FF7F0E")
  ) +
   # scale_fill_discrete(
  #  name = "FS",
  #  labels = c("off" = "Off", "on" = "On")
  #) +
#scale_y_continuous(limits = c(-0.05, 0.18))+
  labs(x = "",
       y = "Peak e-field (V/m)",
       fill = "Freesurfer") +
  
  guides(color = "none") +   # remove duplicate legend

  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        strip.text = element_text(size = 11, face = "bold"),
        strip.background = element_blank(),
        #legend.position = c(0.98, 0.98),
        legend.position = 'none',
        legend.direction = "horizontal",
        legend.justification = c(1, 1),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 10))


# Save figure
ggsave("violin_peak_tms_healthy_anon.png",
       dpi = 300,
       width = 3.5,
       height = 4,
       units = "in")

```



## violin plot, e-field (For paper)

```{r}

# Optional: precompute means per combination
means_df <- sub_data_excl.df %>%
  dplyr::group_by(method, FS) %>%
  dplyr::summarise(mean_E = mean(avg_roi_E_magn, na.rm = TRUE), .groups = "drop_last")

LE_labels <- c(
  "t1" = "T1",
  "t1+t2" = "T1 + T2"
)

ggplot(sub_data_excl.df,
       aes(x = age,
           y = avg_roi_E_magn,
           fill = FS,
           color = FS)) +

  geom_violin(position = position_dodge(width = 0.7),
              alpha = 0.2,
              width = 0.7) +

  geom_jitter(position = position_jitterdodge(jitter.width = 0.15,
                                              dodge.width = 0.7),
              size = 1.5,
              alpha = 0.8) +

  geom_point(data = means_df,
             aes(x = method, y = mean_E, fill = FS),
             shape = 23,
             size = 2.8,
             color = "black",
             position = position_dodge(width = 0.7)) +

  facet_wrap(~ modality, labeller = labeller(modality = LE_labels)) +
  scale_x_discrete(labels = c(
  "t1_t2" = "FS Off",
  "t1_t2_fs" = "FS On"
)) +
  
    scale_fill_discrete(
    name = "FS",
    labels = c("off" = "Off", "on" = "On")
  ) +
#scale_y_continuous(limits = c(-0.05, 0.18))+
  labs(x = "",
       y = "Avg. E-field magnitude (V/m)",
       fill = "Freesurfer") +
  
  guides(color = "none") +   # remove duplicate legend

  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        strip.text = element_text(size = 11, face = "bold"),
        strip.background = element_blank(),
        #legend.position = c(0.98, 0.98),
        legend.position = 'none',
        legend.direction = "horizontal",
        legend.justification = c(1, 1),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 10))


# Save figure
ggsave("violin_magn_healthy.png",
       dpi = 300,
       width = 4,
       height = 4,
       units = "in")


```
## violing plot, peak field

```{r}

# Optional: precompute means per combination
means_df <- sub_data_excl.df %>%
  dplyr::group_by(method, FS) %>%
  dplyr::summarise(mean_E = mean(p99_9, na.rm = TRUE), .groups = "drop_last")

LE_labels <- c(
  "t1" = "T1",
  "t1+t2" = "T1 + T2"
)

ggplot(sub_data_excl.df,
       aes(x = method,
           y = p99_9,
           fill = FS,
           color = FS)) +

  geom_violin(position = position_dodge(width = 0.7),
              alpha = 0.2,
              width = 0.7) +

  geom_jitter(position = position_jitterdodge(jitter.width = 0.15,
                                              dodge.width = 0.7),
              size = 1.5,
              alpha = 0.8) +

  geom_point(data = means_df,
             aes(x = method, y = mean_E, fill = FS),
             shape = 23,
             size = 2.8,
             color = "black",
             position = position_dodge(width = 0.7)) +

  facet_wrap(~ modality, labeller = labeller(modality = LE_labels)) +
  scale_x_discrete(labels = c(
  "t1_t2" = "FS Off",
  "t1_t2_fs" = "FS On"
)) +
  
    scale_fill_discrete(
    name = "FS",
    labels = c("off" = "Off", "on" = "On")
  ) +
#scale_y_continuous(limits = c(-0.05, 0.18))+
  labs(x = "",
       y = "Peak e-field (V/m)",
       fill = "Freesurfer") +
  
  guides(color = "none") +   # remove duplicate legend

  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        strip.text = element_text(size = 11, face = "bold"),
        strip.background = element_blank(),
        #legend.position = c(0.98, 0.98),
        legend.position = 'none',
        legend.direction = "horizontal",
        legend.justification = c(1, 1),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 10))


# Save figure
ggsave("violin_peak_healthy.png",
       dpi = 300,
       width = 4,
       height = 4,
       units = "in")


```

```{r}

```


## violin plot, normal component

```{r}

# Optional: precompute means per combination
means_df <- sub_data_excl.df %>%
  dplyr::group_by(method, FS) %>%
  dplyr::summarise(mean_E = mean(avg_roi_E_normal, na.rm = TRUE), .groups = "drop_last")

LE_labels <- c(
  "t1" = "T1",
  "t1+t2" = "T1 + T2"
)

ggplot(sub_data_excl.df,
       aes(x = method,
           y = avg_roi_E_normal,
           fill = FS,
           color = FS)) +

  geom_violin(position = position_dodge(width = 0.7),
              alpha = 0.2,
              width = 0.7) +

  geom_jitter(position = position_jitterdodge(jitter.width = 0.15,
                                              dodge.width = 0.7),
              size = 1.5,
              alpha = 0.8) +

  geom_point(data = means_df,
             aes(x = method, y = mean_E, fill = FS),
             shape = 23,
             size = 2.8,
             color = "black",
             position = position_dodge(width = 0.7)) +

  facet_wrap(~ modality, labeller = labeller(modality = LE_labels)) +
  scale_x_discrete(labels = c(
  "t1_t2" = "FS Off",
  "t1_t2_fs" = "FS On"
)) +
  
    scale_fill_discrete(
    name = "FS",
    labels = c("off" = "Off", "on" = "On")
  ) +
#scale_y_continuous(limits = c(-0.05, 0.18))+
  labs(x = "",
       y = "Normal component (V/m)",
       fill = "Freesurfer") +
  
  guides(color = "none") +   # remove duplicate legend

  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        strip.text = element_text(size = 11, face = "bold"),
        strip.background = element_blank(),
        #legend.position = c(0.98, 0.98),
        legend.position = 'none',
        legend.direction = "horizontal",
        legend.justification = c(1, 1),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 10))


# Save figure
ggsave("violin_normal_healthy.png",
       dpi = 300,
       width = 4,
       height = 4,
       units = "in")


```


## Peak e-field

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1_t2", "t1_t2_fs")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = p99_9)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = method_f, fill = method_f),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1, 2),
                      labels = c('T1+T2', 'T1+T2+FS')) + #+

   #scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   #scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   #ylim(0.02, 0.25) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

##Normal component

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1_t2", "t1_t2_fs")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = avg_roi_E_normal)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = method_f, fill = method_f),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1, 2),
                      labels = c('T1+T2', 'T1+T2+FS')) + #+

   #scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   #scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   #ylim(0.02, 0.25) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```









```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_all.df %>%
  mutate(method_f = factor(method, levels = c("t1_t2", "t1_t2_le", "t1_t2_fs",  "t1_t2_fs_le")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = avg_roi_E_magn)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = seq_q, fill = seq_q),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3, 4),
                      labels = c('T1+T2', 'T1+T2+Lesion','T1+T2+Fs', 'T1+T2+Fs+Lesion')) +

   scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   #ylim(0.02, 0.25) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1_t2s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

## Peak e-field

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1_t2", "t1_t2_le", "t1_t2_fs",  "t1_t2_fs_le")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = p99_9)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = method_f, fill = method_f),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3, 4),
                      labels = c('T1+T2', 'T1+T2+Lesion','T1+T2+Fs', 'T1+T2+Fs+Lesion')) +

   scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   #ylim(0.18, 0.36) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

## Normal component

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1_t2", "t1_t2_le", "t1_t2_fs",  "t1_t2_fs_le")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = avg_roi_E_normal)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = seq_q, fill = seq_q),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3, 4),
                      labels = c('T1+T2', 'T1+T2+Lesion','T1+T2+Fs', 'T1+T2+Fs+Lesion')) +

   scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   #ylim(0.1, 0.25) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

# Stats analyses

## 1 - Avg. E-field magnitude


```{r}
mod1 <- lmer(avg_roi_E_magn_sc ~
               #Fixed Effects
               FS*grp_age +
               #Random Effects
               (1|subID),
               #Define the data:
               data=sub_data_all.df, REML = TRUE)

summary(mod1)

```

```{r}

report(mod1)

```


## 2 - Normal component


```{r}

mod2 <- lmer(avg_roi_E_normal_sc ~
               #Fixed Effects
               FS*grp_age +
               #Random Effects
               (1|subID),
               #Define the data:
               data=sub_data_all.df, REML = TRUE)

summary(mod2)


```

```{r}

report(mod2)

```

## 3 - Peak e-field

```{r}


mod3 <- lmer(p99_9_sc ~
               #Fixed Effects
               FS*grp_age +
               #Random Effects
               (1|subID),
               #Define the data:
               data=sub_data_all.df, REML = TRUE)

summary(mod3)


```

```{r}
report(mod3)
```


```{r}


results_ef <- t_test(sub_data_all.df, p99_9 ~ FS, paired = TRUE)

results_ef

```



