---
title: 'E-field USC-MUSC dataset - TMS sims'
author: "Diego Arias"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(plyr)
library(dplyr)
library(tidyverse)
library(easystats)
library(ggpubr)
library(ggthemes)
library(Rmisc)
library(readr)
library(lme4)
library(nlme)
library(modelbased)
library(performance)
library(investr) 
library(raincloudplots) # remotes::install_github('jorvlan/raincloudplots')
library(ggstatsplot)
library(paletteer)
library(gtsummary)
library(smplot2)
library(emmeans)
library(ggplot2)
library(rstatix)
library(afex)
library(tidyverse)
library(ggdist)
library(ggthemes)
library(gridExtra)
library(report)

library(minpack.lm) # nlsLM function
library(zoo)

theme_set(theme_classic())

dir <- '/Users/ariasd/Library/CloudStorage/OneDrive-MedicalUniversityofSouthCarolina/Documents/GitHub/StrokeEfield_USC/data_matrices/TMS/'
dir_ex <- '/Users/ariasd/Library/CloudStorage/OneDrive-MedicalUniversityofSouthCarolina/Documents/GitHub/StrokeEfield_USC/data_matrices/excluded/adj'

# 1- Load e-fields magnitudes for T1 only

fullpath <- file.path(dir, 'charm_T1_csf_noneck_sform_adj_Emagn.csv')

t1.df <- read.csv(fullpath)
t1.df$method <- 't1'
t1.df$modality <- 't1'
t1.df$FS <- 'off'
t1.df$LE <- 'off'

t1.df$seq_q <- c("Good", "Fair", "Fair", "Poor", "Poor",
"Good", "Poor", "Good", "Fair", "Poor",
"Poor", "Fair", "Fair", "Poor", "Poor",
"Fair", "Poor", "Good", "Poor", "Poor",
"Poor", "Good", "Poor", "Good", "Poor",
"Fair", "Fair", "Poor", "Good", "Poor")


# 2- Load e-fields magnitudes for T1 + Freesurfer 

fullpath <- file.path(dir, 'charm_T1_csf_noneck_sform_fs_adj_Emagn.csv')
#fullpath_ex <- file.path(dir_ex, 'charm_T1_csf_noneck_sform_fs_adj_Emagn.csv')

t1_fs.df <- read.csv(fullpath)
t1_fs.df$method <- 't1_fs'
t1_fs.df$modality <- 't1'
t1_fs.df$FS <- 'on'
t1_fs.df$LE <- 'off'

t1_fs.df$seq_q <- c("Good", "Good", "Good", "Good", "Fair",
"Good", "Fair", "Good", "Good", "Good",
"Good", "Good", "Good", "Good", "Good",
"Good", "Poor", "Good", "Good", "Good",
"Good", "Good", "NaN", "Good", "Fair",
"Good", "Good", "Poor", "Good", "Good")
  
# 3- Load e-fields magnitudes for T1 + lesion

fullpath <- file.path(dir, 'charm_T1_csf_noneck_sform_lesion_adj_Emagn.csv')

t1_le.df <- read.csv(fullpath)
t1_le.df$method <- 't1_le'
t1_le.df$modality <- 't1'
t1_le.df$FS <- 'off'
t1_le.df$LE <- 'on'


# 4- Load e-fields magnitudes for T1 + lesion + Freesurfer

fullpath <- file.path(dir, 'charm_T1_csf_noneck_sform_fs_lesion_adj_Emagn.csv')

t1_fs_le.df <- read.csv(fullpath)
t1_fs_le.df$method <- 't1_fs_le'
t1_fs_le.df$modality <- 't1'
t1_fs_le.df$FS <- 'on'
t1_fs_le.df$LE <- 'on'

# 5- Load e-fields magnitudes for T1+T2

fullpath <- file.path(dir, 'charm_T1_T2_csf_noneck_sform_adj_Emagn.csv')

t1_t2.df <- read.csv(fullpath)
t1_t2.df$method <- 't1_t2'
t1_t2.df$modality <- 't1+t2'
t1_t2.df$FS <- 'off'
t1_t2.df$LE <- 'off'
t1_t2.df$seq_q <- c("Good", "Fair", "Fair", "Fair", "Fair",
"Good", "Fair", "Good", "Good", "Fair",
"Poor", "Good", "Good", "Fair", "Poor",
"Fair", "Poor", "Good", "Poor", "Fair", 
"Fair", "Good", "Fair", "Good", "Good",
"Fair", "Good", "Poor", "Good", "Good")

# 6- load e-fields magnitudes for T1+T2+lesion

fullpath <- file.path(dir, 'charm_T1_T2_csf_noneck_sform_lesion_adj_Emagn.csv')

t1_t2_le.df <- read.csv(fullpath)
t1_t2_le.df$method <- 't1_t2_le'
t1_t2_le.df$modality <- 't1+t2'
t1_t2_le.df$FS <- 'off'
t1_t2_le.df$LE <- 'on'


# 7- load e-fields magnitudes for T1+T2+Freesurfer

fullpath <- file.path(dir, 'charm_T1_T2_csf_noneck_sform_fs_adj_Emagn.csv')

t1_t2_fs.df <- read.csv(fullpath)
t1_t2_fs.df$method <- 't1_t2_fs'
t1_t2_fs.df$modality <- 't1+t2'
t1_t2_fs.df$FS <- 'on'
t1_t2_fs.df$LE <- 'off'

t1_t2_fs.df$seq_q <- c("Good", "Good", "Good", "Good", "Good",
"Good", "Good", "Good", "Good", "Good",
"Good", "Good", "Good", "Good", "Good",
"Good", "Poor", "Good", "Good", "Good",
"Good", "Good", "Nan", "Good", "Good",
"Good", "Good", "Poor", "Good", "Good")

# 8- load e-fields magnitudes for T1+T2+Freesurfer+le

fullpath <- file.path(dir, 'charm_T1_T2_csf_noneck_sform_fs_lesion_adj_Emagn.csv')

t1_t2_fs_le.df <- read.csv(fullpath)
t1_t2_fs_le.df$method <- 't1_t2_fs_le'
t1_t2_fs_le.df$modality <- 't1+t2'
t1_t2_fs_le.df$FS <- 'on'
t1_t2_fs_le.df$LE <- 'on'


data.df <- bind_rows(t1.df, t1_fs.df, t1_le.df, t1_fs_le.df, t1_t2.df, t1_t2_fs.df, t1_t2_le.df, t1_t2_fs_le.df)

#data.df <- bind_rows(t1.df, t1_fs.df, t1_le.df, t1_fs_le.df)

data_all.df <- data.df
#data.df <- bind_rows(t1.df, t1_fs.df, t1_le.df, t1_fs_le.df,  
#                     t1_t2.df, t1_t2_fs.df, t1_t2_le.df, t1_t2_fs_le.df)

#data.df <- data.df %>%
#  mutate(avg_E_magn = as.numeric(avg_E_magn),
#         avg_E_normal = as.numeric(avg_E_normal),
#         avg_E_tanget = as.numeric(avg_E_tanget),
##         n_nodes_roi = as.numeric(n_nodes_roi),
#         n_nodes_surf = as.numeric(n_nodes_surf))

#str(data.df)


  #filter(subID != '216' & subID != '195' & subID != '218' & subID != '125')  
#filter(subID != '142' &  subID != '168' & subID != '188' & subID != '209' & subID != '213'  & subID != '222' )

#sub_data_wide <- sub_data_excl.df %>%
#   pivot_wider(
#     names_from = method,       # Column with categories to become new columns
#     values_from = c(avg_roi_E_magn, avg_roi_E_normal, avg_roi_E_tangent)      # Column with values to populate these columns
     
#   )

# define factors

#sub_data_excl.df$modality <-factor(sub_data_excl.df$modality)
#sub_data_excl.df$FS <-factor(sub_data_excl.df$FS)
#sub_data_excl.df$LE <-factor(sub_data_excl.df$LE)

sub_data_excl.df <- data.df #%>%
sub_data_all.df <-data_all.df

scale_factor = 1.2*(150/2) # di/dt at MSO for cool-B65 AP coil
sub_data_all.df$avg_roi_E_magn_sc <- sub_data_all.df$avg_roi_E_magn*scale_factor
sub_data_all.df$avg_roi_E_normal_sc <- sub_data_all.df$avg_roi_E_normal*scale_factor
sub_data_all.df$p99_9_sc <- sub_data_all.df$p99_9*scale_factor

#sub_data_all.df$age_c <-scale(sub_data_all.df$age,
#                              center = TRUE,
#                              scale = FALSE)

sub_data_all.df$modality <-factor(sub_data_all.df$modality)
sub_data_all.df$FS <-factor(sub_data_all.df$FS)
sub_data_all.df$LE <-factor(sub_data_all.df$LE)

```

### Fluvial plot (Figure 2)

```{r}
library(ggalluvial)



quality_sub <- sub_data_all.df %>%
  filter(method %in% c("t1", "t1_t2", "t1_fs", "t1_t2_fs")) %>%
    # remove subjects with ANY NA or NaN in seq_q
  # 🔴 convert safely first
  mutate(seq_q = as.character(seq_q)) %>%
  
  group_by(subID) %>%
  
  # 🔴 remove subject if ANY invalid value exists
  filter(!any(is.na(seq_q) | seq_q == "NaN")) %>%
  
  ungroup() %>%
  mutate(
    method = factor(
      method,
      levels = c("t1", "t1_t2", "t1_fs", "t1_t2_fs")
    ),
    seq_q = factor(
      seq_q,
      levels = c("Poor", "Fair", "Good")
    )
  )

  n_sub <- n_distinct(quality_sub$subID)

ggplot(
  quality_sub,
  aes(
    x = method,
    stratum = seq_q,
    alluvium = subID,
    fill = seq_q,
    label = seq_q
  )
  
) +
  geom_flow(alpha = 0.5) +
  geom_stratum() +
  scale_fill_manual(
  breaks = c("Poor", "Fair", "Good"),
  values = c(
    "Poor" = "#D73027",
    "Fair" = "#FDAE61",
    "Good" = "#1A9850"
  )) +
    
     scale_x_discrete(
                      labels = c('T1', 'T1+T2','T1+FS', 'T1+T2+FS')) #+

  scale_y_continuous(
  labels = scales::label_percent(scale = 100 / n_sub),
  limits = c(0, 100),
  breaks = seq(0, 100, 20)#,
  #labels = function(x) paste0(x, "%")
)
#   + theme_classic()

```


# All T1s combinations

T1, T1+Lesion, T1+Freesurfer, T1+Freesurfer+Lesion

\*Freesurfer was generated based only the T1

## E-field magnitude

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1", "t1_le", "t1_fs",  "t1_fs_le")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = avg_roi_E_magn)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = method_f, fill = method_f),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1, 2, 3, 4),
                      labels = c('T1', 'T1+Lesion','T1+Fs', 'T1+Fs+Lesion')) + #+

   #scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   #scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   #ylim(0.02, 0.25) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```



## Peak e-field

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1", "t1_le", "t1_fs",  "t1_fs_le")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = p99_9)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = method_f, fill = method_f),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3, 4),
                      labels = c('T1', 'T1+Lesion','T1+Fs', 'T1+Fs+Lesion')) +

  # scale_fill_manual(values = c("#6D8325FF", 'red') + #"#E5AD4FFF")) +
  # scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
  #ylim(0.18, 0.36) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

## Normal component

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1", "t1_le", "t1_fs",  "t1_fs_le")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = avg_roi_E_normal)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = method_f, fill = method_f),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3, 4),
                      labels = c('T1', 'T1+Lesion','T1+Fs', 'T1+Fs+Lesion')) +

  # scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   #scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   #ylim(0.1, 0.25) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

# All T1+T2 combinations

T1+T2, T1+T2+Lesion, T1+T2+Freesurfer, T1+T2+Freesurfer+Lesion

\*Freesurfer was generated based on the T1 and T2

## E-field magnitude

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1_t2", "t1_t2_le", "t1_t2_fs",  "t1_t2_fs_le")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = avg_roi_E_magn)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = method_f, fill = method_f),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3, 4),
                      labels = c('T1+T2', 'T1+T2+Lesion','T1+T2+Fs', 'T1+T2+Fs+Lesion')) +

  # scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
 #  scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   #ylim(0.02, 0.25) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1_t2s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_all.df %>%
  mutate(method_f = factor(method, levels = c("t1_t2", "t1_t2_le", "t1_t2_fs",  "t1_t2_fs_le")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = avg_roi_E_magn)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = seq_q, fill = seq_q),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3, 4),
                      labels = c('T1+T2', 'T1+T2+Lesion','T1+T2+Fs', 'T1+T2+Fs+Lesion')) +

   scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   #ylim(0.02, 0.25) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1_t2s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

## Peak e-field

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1_t2", "t1_t2_le", "t1_t2_fs",  "t1_t2_fs_le")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = p99_9)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = method_f, fill = method_f),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3, 4),
                      labels = c('T1+T2', 'T1+T2+Lesion','T1+T2+Fs', 'T1+T2+Fs+Lesion')) +

   scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   #ylim(0.18, 0.36) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

## Normal component

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1_t2", "t1_t2_le", "t1_t2_fs",  "t1_t2_fs_le")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = avg_roi_E_normal)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = seq_q, fill = seq_q),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3, 4),
                      labels = c('T1+T2', 'T1+T2+Lesion','T1+T2+Fs', 'T1+T2+Fs+Lesion')) +

   scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   #ylim(0.1, 0.25) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

# Effect of Freesurfer on e-field estimates

Target: anode position individualized based on fMRI

T1, T1+T2 vs T1+FS, T1+T2+FS (no lesion considered)

Obs: Incorporate the lesion increase the inter individual variability of the e-field estimates.

## E-field magnitude

### Only completed datasets.184 simulations included

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1", "t1_t2", "t1_fs", "t1_t2_fs")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = avg_roi_E_magn)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = method_f, fill = method_f),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3, 4),
                      labels = c('T1', 'T1+T2', 'T1+FS', 'T1+T2+FS')) +

   #scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   #scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   #ylim(0.02, 0.35) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

### All. Incompleted data sets included

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_all.df %>%
  mutate(method_f = factor(method, levels = c("t1", "t1_t2", "t1_fs", "t1_t2_fs")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = avg_roi_E_magn)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = seq_q, fill = seq_q),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3, 4),
                      labels = c('T1', 'T1+T2', 'T1+FS', 'T1+T2+FS')) +

   scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   ylim(0.02, 0.35) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

## Peak e-field

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1", "t1_t2", "t1_fs", "t1_t2_fs")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = p99_9)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = seq_q, fill = seq_q),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3, 4),
                      labels = c('T1', 'T1+T2', 'T1+FS', 'T1+T2+FS')) +

   scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
  ylim(0.18, 0.36) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

## Normal component

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1", "t1_t2", "t1_fs", "t1_t2_fs")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = avg_roi_E_normal)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = seq_q, fill = seq_q),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3, 4),
                      labels = c('T1', 'T1+T2', 'T1+FS', 'T1+T2+FS')) +

   scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   #ylim(0.02, 0.25) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

# Effect of Lesion on e-field (anode position individualized)

T1, T1+T2 vs T1+le, T1+T2+le (no lesion considered)

Obs: Incorporate the lesion increase the inter individual variability of the e-field estimates.

## E-field magnitude

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1", "t1_t2", "t1_le", "t1_t2_le")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = avg_roi_E_magn)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = seq_q, fill = seq_q),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3, 4),
                      labels = c('T1', 'T1+T2', 'T1+T2+LE', 'T1+T2+LE')) +

   scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   ylim(0.02, 0.25) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

## Peak e-fied

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1", "t1_t2", "t1_le", "t1_t2_le")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = p99_9)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = seq_q, fill = seq_q),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3, 4),
                      labels = c('T1', 'T1+T2', 'T1+T2+LE', 'T1+T2+LE')) +

   scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   ylim(0.18, 0.36) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

## Normal component

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1", "t1_t2", "t1_le", "t1_t2_le")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = avg_roi_E_normal)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = seq_q, fill = seq_q),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3, 4),
                      labels = c('T1', 'T1+T2', 'T1+LE', 'T1+T2+LE')) +

   scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   #ylim(0.02, 0.25) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

# Effect of Lesion on e-field including Freesurfer

T1+fs, T1+T2+fs vs T1+fs+le, T1+T2+fs+le (no lesion considered) including in Freesurfer

Obs: Same patter in observed when we incoporate freesurfer pial surfaces into the model. Incorporate the lesion increase the inter individual variability of the e-field estimates.

## E-field magnitude

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1_fs", "t1_t2_fs", "t1_fs_le", "t1_t2_fs_le")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = avg_roi_E_magn)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = seq_q, fill = seq_q),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3,4),
                      labels = c('T1+fs', 'T1+T2+fs', 'T1+fs+LE', 'T1+T2+fs+LE')) +

   scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   ylim(0.02, 0.25) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

## Peak e-field

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1_fs", "t1_t2_fs", "t1_fs_le", "t1_t2_fs_le")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = p99_9)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = seq_q, fill = seq_q),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3,4),
                      labels = c('T1+fs', 'T1+T2+fs', 'T1+fs+LE', 'T1+T2+fs+LE')) +

   scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   ylim(0.18, 0.36) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

## Normal component

```{r, echo=FALSE}

set.seed(123)  # reproducible jitter

# 1. Determine the x-axis ordering of methods
#ordered_methods <- sub_data.df %>%
#  group_by(method) %>%
#  summarize(mean_val = mean(avg_roi_E_magn, na.rm = TRUE)) %>%
#  arrange(mean_val) %>%
#  pull(method)

# 2. Add numeric x position + deterministic jitter
jitter_width <- 0.1

data2 <- sub_data_excl.df %>%
  mutate(method_f = factor(method, levels = c("t1_fs", "t1_t2_fs", "t1_fs_le", "t1_t2_fs_le")),
         x_base = as.numeric(method_f),
         x_jitter = x_base + runif(n(), -jitter_width, jitter_width)) %>%
  arrange(subID, x_base)  # ensures lines connect in order

#data2$method_f <- factor(data2$method_f, levels = c("t1", "t1_le"))
#data2$seq_q <- factor(data2$seq_q, levels = c("Good", "Poor"))
# 3. Plot
ggplot(data2, aes(y = avg_roi_E_normal)) +
  
  # boxplots at integer positions
  geom_boxplot(aes(x = x_base, group = method_f),
               color = "black", outlier.shape = NA, alpha = 0.5, width = 0.3) +
  
   # gray lines connecting jittered points per subject
   geom_path(aes(x = x_jitter, group = subID),
             colour = "gray70", alpha = 0.5, size = 0.5) +
   
#   # jittered points
   geom_point(aes(x = x_jitter, colour = seq_q, fill = seq_q),
              shape = 21, alpha = 0.6, size = 2, position = "identity") +
   
#group mean (at base positions, not jittered)
   stat_summary(aes(x = x_base, group = method_f),
                fun = mean, geom = "point",
                shape = 20, size = 2, color = "black", fill = "black") +

   # x-axis labels
   scale_x_continuous(breaks = c(1,2,3,4),
                      labels = c('T1+fs', 'T1+T2+fs', 'T1+fs+LE', 'T1+T2+fs+LE')) +

   scale_fill_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +
   scale_color_manual(values = c("#6D8325FF", 'red')) + #"#E5AD4FFF")) +

   labs(x = "", y = "E-field magnitude (V/m)",
        caption = "black circle is the group mean") +
   #ylim(0.02, 0.25) +
   theme(axis.text.x = element_text(size = 11))

  #Save last plot as PNG
 ggsave("all_t1s.png", dpi = 300, width = 5.5, height = 4, units = "in")

```

# Stats analyses

Preliminary analyses on 23 subjects (not including exclusions)

Fixed effects: Modality (T1 or T1+T2), Freesurfer (On or Off), Lesion Mask (On or Off)

Random effects: Subjects

Results: Statistically significant effects for Freesurfer and Lesion Mask, no interactions.

## 1 - Avg. E-field magnitude

### a) Linear mixed-effect model

```{r}

mod1 <- lmer(avg_roi_E_magn_sc ~
               #Fixed Effects
               modality*FS*LE +
               #Random Effects
               (1|subID),
               #Define the data:
               data=sub_data_all.df, REML = TRUE)

summary(mod1)

```
### b) Stats report 

```{r}

report(mod1)

```

###c) Marginal means

```{r}

# Get estimated marginal means for all 3 factors
emm_main <- emmeans(mod1, ~ modality * FS * LE)
emm_df   <- as.data.frame(emm_main)

# Plot with FS as color and LE as dodge (side-by-side)
ggplot(emm_df, aes(x = modality, y = emmean, color = FS, group = FS)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +
  geom_errorbar(
    aes(ymin = lower.CL, ymax = upper.CL),
    width = 0.1,
    position = position_dodge(width = 0.3)
  ) +
  facet_wrap(~ LE, labeller = labeller(LE = c("off" = "Lesion Off", "on" = "Lesion On"))) +
  labs(
    x = "Structural modality",
    y = "Mean |E| (V/m)",
    color = "Freesurfer"
  ) +
  theme_classic()

```



#### Violin plot (184 simulations) - alternative

```{r, echo=FALSE}

# Optional: precompute means per combination
means_df <- sub_data_all.df %>%
  dplyr::group_by(modality, FS, LE) %>%
  dplyr::summarise(mean_E = mean(avg_roi_E_magn_sc, na.rm = TRUE), .groups = "drop_last")

LE_labels <- c(
  "t1" = "T1",
  "t1+t2" = "T1 + T2"
)

ggplot(sub_data_all.df,
       aes(x = LE,
           y = avg_roi_E_magn_sc,
           fill = FS,
           color = FS)) +

  geom_violin(position = position_dodge(width = 0.7),
              alpha = 0.2,
              width = 0.7) +

  geom_jitter(position = position_jitterdodge(jitter.width = 0.15,
                                              dodge.width = 0.7),
              size = 1.5,
              alpha = 0.8) +

  geom_point(data = means_df,
             aes(x = LE, y = mean_E, fill = FS),
             shape = 23,
             size = 2.8,
             color = "black",
             position = position_dodge(width = 0.7)) +

  facet_wrap(~ modality, labeller = labeller(modality = LE_labels)) +
  scale_x_discrete(labels = c(
  "on" = "LE On",
  "off" = "LE Off"
)) +
 
  
     scale_fill_manual(
    values = c("off" = "#1F77B4",   # blue
               "on"  = "#FF7F0E"),  # orange
    name = "FS",
    labels = c("off" = "Off",
               "on"  = "On")
  ) +

  scale_color_manual(
    values = c("off" = "#1F77B4",
               "on"  = "#FF7F0E")
  ) + 
 #   scale_fill_discrete(
#    name = "FS",
 #   labels = c("off" = "Off", "on" = "On")
#  ) +

  labs(x = "",
       y = "Avg. E-field magnitude (V/m)",
       fill = "Freesurfer") +
  
  guides(color = "none") +   # remove duplicate legend

  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        strip.text = element_text(size = 11, face = "bold"),
        strip.background = element_blank(),
        #legend.position = c(0.98, 0.98),
        legend.position = 'none',
        legend.direction = "horizontal",
        legend.justification = c(1, 1),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 10))


# Save figure
ggsave("violin_eMagn_stroke.png",
       dpi = 300,
       width = 5.5,
       height = 4,
       units = "in")


```


# 2- Peak e-field

### a) Linear mixed-effect model (230 sim)

Results: Statistically significant results only for Freesurfer


```{r}
mod2 <- lmer(p99_9_sc ~
               #Fixed Effects
               modality*FS*LE +
               #Random Effects
               (1|subID),
               #Define the data:
               data=sub_data_all.df, REML = TRUE)

summary(mod2)
```
### b) Stats report
```{r}

report(mod2)

```

###c) marginal means

```{r}

# Get estimated marginal means for all 3 factors
emm_main <- emmeans(mod2, ~ modality * FS * LE)
emm_df   <- as.data.frame(emm_main)

# Plot with FS as color and LE as dodge (side-by-side)
ggplot(emm_df, aes(x = modality, y = emmean, color = FS, group = FS)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +
  geom_errorbar(
    aes(ymin = lower.CL, ymax = upper.CL),
    width = 0.1,
    position = position_dodge(width = 0.3)
  ) +
  facet_wrap(~ LE, labeller = labeller(LE = c("off" = "Lesion Off", "on" = "Lesion On"))) +
  labs(
    x = "Structural modality",
    y = "Mean |E| (V/m)",
    color = "FreeSurfer"
  ) +
  theme_classic()
```




###d) violin plot - alternative

```{r, echo=FALSE}

# Optional: precompute means per combination
means_df <- sub_data_all.df %>%
  dplyr::group_by(modality, FS, LE) %>%
  dplyr::summarise(mean_E = mean(p99_9_sc, na.rm = TRUE), .groups = "drop_last")

LE_labels <- c(
  "t1" = "T1",
  "t1+t2" = "T1 + T2"
)

ggplot(sub_data_all.df,
       aes(x = LE,
           y = p99_9_sc,
           fill = FS,
           color = FS)) +

  geom_violin(position = position_dodge(width = 0.7),
              alpha = 0.2,
              width = 0.7) +

  geom_jitter(position = position_jitterdodge(jitter.width = 0.15,
                                              dodge.width = 0.7),
              size = 1.5,
              alpha = 0.8) +

  geom_point(data = means_df,
             aes(x = LE, y = mean_E, fill = FS),
             shape = 23,
             size = 2.8,
             color = "black",
             position = position_dodge(width = 0.7)) +

  facet_wrap(~ modality, labeller = labeller(modality = LE_labels)) +
  scale_x_discrete(labels = c(
  "on" = "LE yes",
  "off" = "LE no"
)) +
  
    #scale_fill_discrete(
    #name = "FS",
    #labels = c("off" = "Off", "on" = "On")
  #) +

     scale_fill_manual(
    values = c("off" = "#1F77B4",   # blue
               "on"  = "#FF7F0E"),  # orange
    name = "FS",
    labels = c("off" = "no",
               "on"  = "yes")
  ) +

  scale_color_manual(
    values = c("off" = "#1F77B4",
               "on"  = "#FF7F0E")
  ) +
  labs(x = "",
       y = "Peak e-field (V/m)",
       fill = "Freesurfer") +
  
  guides(color = "none") +   # remove duplicate legend

  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        strip.text = element_text(size = 11, face = "bold"),
        strip.background = element_blank(),
        #legend.position = c(0.98, 0.98),
        legend.position = 'none',
        legend.direction = "horizontal",
        legend.justification = c(1, 1),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 10))


# Save figure
ggsave("violin_peak_stroke.png",
       dpi = 300,
       width = 5.5,
       height = 4,
       units = "in")


```



# 3- Normal component

### Linear mixed-effect model (184 sim)

Results: Statistically significant differences for Freesurfer and lesion

```{r}

mod3 <- lmer(avg_roi_E_normal_sc ~
               #Fixed Effects
               modality*FS*LE +
               #Random Effects
               (1|subID),
               #Define the data:
               data=sub_data_all.df, REML = TRUE)

summary(mod3)

```
```{r}

report(mod3)

```

#### marginal means

```{r}

# Get estimated marginal means for all 3 factors
emm_main <- emmeans(mod3, ~ modality * FS * LE)
emm_df   <- as.data.frame(emm_main)

# Plot with FS as color and LE as dodge (side-by-side)
ggplot(emm_df, aes(x = modality, y = emmean, color = FS, group = FS)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +
  geom_errorbar(
    aes(ymin = lower.CL, ymax = upper.CL),
    width = 0.1,
    position = position_dodge(width = 0.3)
  ) +
  facet_wrap(~ LE, labeller = labeller(LE = c("off" = "Lesion Off", "on" = "Lesion On"))) +
  labs(
    x = "Structural modality",
    y = "Mean |E| (V/m)",
    color = "FreeSurfer"
  ) +
  theme_classic()

```

#### violin plot for manuscript

```{r}

# Optional: precompute means per combination
means_df <- sub_data_all.df %>%
  dplyr::group_by(modality, FS, LE) %>%
  dplyr::summarise(mean_E = mean(avg_roi_E_normal_sc, na.rm = TRUE), .groups = "drop_last")

LE_labels <- c(
  "t1" = "T1",
  "t1+t2" = "T1 + T2"
)

ggplot(sub_data_all.df,
       aes(x = LE,
           y = avg_roi_E_normal_sc,
           fill = FS,
           color = FS)) +

  geom_violin(position = position_dodge(width = 0.7),
              alpha = 0.2,
              width = 0.7) +

  geom_jitter(position = position_jitterdodge(jitter.width = 0.15,
                                              dodge.width = 0.7),
              size = 1.5,
              alpha = 0.8) +

  geom_point(data = means_df,
             aes(x = LE, y = mean_E, fill = FS),
             shape = 23,
             size = 2.8,
             color = "black",
             position = position_dodge(width = 0.7)) +

  facet_wrap(~ modality, labeller = labeller(modality = LE_labels)) +
  scale_x_discrete(labels = c(
  "on" = "LE On",
  "off" = "LE Off"
)) +
  
   # scale_fill_discrete(
    #name = "FS",
   # labels = c("off" = "Off", "on" = "On")
#  ) +
  
     scale_fill_manual(
    values = c("off" = "#1F77B4",   # blue
               "on"  = "#FF7F0E"),  # orange
    name = "FS",
    labels = c("off" = "Off",
               "on"  = "On")
  ) +

  scale_color_manual(
    values = c("off" = "#1F77B4",
               "on"  = "#FF7F0E")
  ) +
#scale_y_continuous(limits = c(-0.05, 0.18))+
  labs(x = "",
       y = "Normal component (V/m)",
       fill = "Freesurfer") +
  
  guides(color = "none") +   # remove duplicate legend

  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        strip.text = element_text(size = 11, face = "bold"),
        strip.background = element_blank(),
        #legend.position = c(0.98, 0.98),
        legend.position = 'none',
        legend.direction = "horizontal",
        legend.justification = c(1, 1),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 10))


# Save figure
ggsave("violin_normal_stroke.png",
       dpi = 300,
       width = 5.5,
       height = 4,
       units = "in")

```



