---
title: 'E-field analysis stroke tDCS'
author: "Diego Arias, PhD"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE, warning=FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(plyr)
library(dplyr)
library(tidyverse)
library(easystats)
library(ggpubr)
library(ggthemes)
library(Rmisc)
library(readr)
library(lme4)
library(nlme)
library(modelbased)
library(performance)
library(investr) 
library(raincloudplots) # remotes::install_github('jorvlan/raincloudplots')
library(ggstatsplot)
library(paletteer)
library(gtsummary)
library(smplot2)
library(emmeans)
library(ggplot2)
library(rstatix)
library(afex)
library(tidyverse)
library(ggdist)
library(ggthemes)
library(gridExtra)
library(report)
library(minpack.lm) # nlsLM function
library(zoo)

theme_set(theme_classic())

# add your own directory
dir <- '/Users/ariasd/Library/CloudStorage/OneDrive-MedicalUniversityofSouthCarolina/Documents/GitHub/stroke_efield_musc_usc/data/stroke/tDCS'

# 1- Load e-fields magnitudes for T1 only

fullpath <- file.path(dir, 'charm_T1_csf_noneck_sform_adj_Emagn.csv')

t1.df <- read.csv(fullpath)
t1.df$method <- 't1'
t1.df$modality <- 't1'
t1.df$FS <- 'off'
t1.df$LE <- 'off'

# 2- Load e-fields magnitudes for T1 + Freesurfer 

fullpath <- file.path(dir, 'charm_T1_csf_noneck_sform_fs_adj_Emagn.csv')

t1_fs.df <- read.csv(fullpath)
t1_fs.df$method <- 't1_fs'
t1_fs.df$modality <- 't1'
t1_fs.df$FS <- 'on'
t1_fs.df$LE <- 'off'

# 3- Load e-fields magnitudes for T1 + lesion

fullpath <- file.path(dir, 'charm_T1_csf_noneck_sform_lesion_adj_Emagn.csv')

t1_le.df <- read.csv(fullpath)
t1_le.df$method <- 't1_le'
t1_le.df$modality <- 't1'
t1_le.df$FS <- 'off'
t1_le.df$LE <- 'on'

# 4- Load e-fields magnitudes for T1 + lesion + Freesurfer

fullpath <- file.path(dir, 'charm_T1_csf_noneck_sform_fs_lesion_adj_Emagn.csv')

t1_fs_le.df <- read.csv(fullpath)
t1_fs_le.df$method <- 't1_fs_le'
t1_fs_le.df$modality <- 't1'
t1_fs_le.df$FS <- 'on'
t1_fs_le.df$LE <- 'on'

# 5- Load e-fields magnitudes for T1+T2

fullpath <- file.path(dir, 'charm_T1_T2_csf_noneck_sform_adj_Emagn.csv')

t1_t2.df <- read.csv(fullpath)
t1_t2.df$method <- 't1_t2'
t1_t2.df$modality <- 't1+t2'
t1_t2.df$FS <- 'off'
t1_t2.df$LE <- 'off'

# 6- load e-fields magnitudes for T1+T2+lesion

fullpath <- file.path(dir, 'charm_T1_T2_csf_noneck_sform_lesion_adj_Emagn.csv')

t1_t2_le.df <- read.csv(fullpath)
t1_t2_le.df$method <- 't1_t2_le'
t1_t2_le.df$modality <- 't1+t2'
t1_t2_le.df$FS <- 'off'
t1_t2_le.df$LE <- 'on'

# 7- load e-fields magnitudes for T1+T2+Freesurfer

fullpath <- file.path(dir, 'charm_T1_T2_csf_noneck_sform_fs_adj_Emagn.csv')

t1_t2_fs.df <- read.csv(fullpath)
t1_t2_fs.df$method <- 't1_t2_fs'
t1_t2_fs.df$modality <- 't1+t2'
t1_t2_fs.df$FS <- 'on'
t1_t2_fs.df$LE <- 'off'

# 8- load e-fields magnitudes for T1+T2+Freesurfer+le

fullpath <- file.path(dir, 'charm_T1_T2_csf_noneck_sform_fs_lesion_adj_Emagn.csv')

t1_t2_fs_le.df <- read.csv(fullpath)
t1_t2_fs_le.df$method <- 't1_t2_fs_le'
t1_t2_fs_le.df$modality <- 't1+t2'
t1_t2_fs_le.df$FS <- 'on'
t1_t2_fs_le.df$LE <- 'on'

data.df <- bind_rows(t1.df, t1_fs.df, t1_le.df, t1_fs_le.df,  
                     t1_t2.df, t1_t2_fs.df, t1_t2_le.df, t1_t2_fs_le.df)

sub_data_all.df <- data.df
  
sub_data_all.df$modality <- factor(sub_data_all.df$modality)
sub_data_all.df$FS <- factor(sub_data_all.df$FS)
sub_data_all.df$LE <- factor(sub_data_all.df$LE)

```
# Stats analyses

Fixed effects: Modality (T1 or T1+T2), Freesurfer (Yes or No), Lesion Mask (Yes or No)

Random effects: Subjects

Results: Statistically significant effects for Freesurfer and Lesion Mask, no interactions.

# 1 - Avg. E-field magnitude

### a) Linear mixed-effect model

```{r}

mod1 <- lmer(avg_roi_E_magn ~
               #Fixed Effects
               modality*FS*LE +
               #Random Effects
               (1|subID),
               #Define the data:
               data=sub_data_all.df, REML = TRUE)

summary(mod1)

```

### b) Stats report

```{r}

report(mod1)

```

### c) Marginal means


```{r, echo=FALSE}

# Get estimated marginal means for all 3 factors
emm_main <- emmeans(mod1, ~ modality * FS * LE)
emm_df   <- as.data.frame(emm_main)

# Plot with FS as color and LE as dodge (side-by-side)
ggplot(emm_df, aes(x = modality, y = emmean, color = FS, group = FS)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +
  geom_errorbar(
    aes(ymin = lower.CL, ymax = upper.CL),
    width = 0.1,
    position = position_dodge(width = 0.3)
  ) +
  facet_wrap(~ LE, labeller = labeller(LE = c("off" = "Lesion Off", "on" = "Lesion On"))) +
  labs(
    x = "Structural modality",
    y = "Mean |E| (V/m)",
    color = "Freesurfer"
  ) +
  theme_classic()

```


### d) Violin plot 

```{r, echo=FALSE}

# Optional: precompute means per combination
means_df <- sub_data_all.df %>%
  dplyr::group_by(modality, FS, LE) %>%
  dplyr::summarise(mean_E = mean(avg_roi_E_magn, na.rm = TRUE), .groups = "drop_last")

LE_labels <- c(
  "t1" = "T1",
  "t1+t2" = "T1 + T2"
)

ggplot(sub_data_all.df,
       aes(x = LE,
           y = avg_roi_E_magn,
           fill = FS,
           color = FS)) +

  geom_violin(position = position_dodge(width = 0.7),
              alpha = 0.2,
              width = 0.7) +

  geom_jitter(position = position_jitterdodge(jitter.width = 0.15,
                                              dodge.width = 0.7),
              size = 1.5,
              alpha = 0.8) +

  geom_point(data = means_df,
             aes(x = LE, y = mean_E, fill = FS),
             shape = 23,
             size = 2.8,
             color = "black",
             position = position_dodge(width = 0.7)) +

  facet_wrap(~ modality, labeller = labeller(modality = LE_labels)) +
  scale_x_discrete(labels = c(
  "on" = "LE yes",
  "off" = "LE on"
)) +
  
    scale_fill_discrete(
    name = "FS",
    labels = c("off" = "no", "on" = "yes")
  ) +

  labs(x = "",
       y = "Avg. E-field magnitude (V/m)",
       fill = "Freesurfer") +
  
  guides(color = "none") +   # remove duplicate legend

  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        strip.text = element_text(size = 11, face = "bold"),
        strip.background = element_blank(),
        #legend.position = c(0.98, 0.98),
        legend.position = 'none',
        legend.direction = "horizontal",
        legend.justification = c(1, 1),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 10))


# Save figure
ggsave("violin_eMagn.png",
       dpi = 300,
       width = 5.5,
       height = 4,
       units = "in")


```


# 2 - Peak e-field

### a) Linear mixed-effect model

Results: Statistically significant results only for Freesurfer


```{r}
mod2 <- lmer(p99_9 ~
               #Fixed Effects
               modality*FS*LE +
               #Random Effects
               (1|subID),
               #Define the data:
               data=sub_data_all.df, REML = TRUE)

summary(mod2)

```

### b) Stats report

```{r}

report(mod2)

```

### c) Marginal means

```{r, echo=FALSE}

# Get estimated marginal means for all 3 factors
emm_main <- emmeans(mod2, ~ modality * FS * LE)
emm_df   <- as.data.frame(emm_main)

# Plot with FS as color and LE as dodge (side-by-side)
ggplot(emm_df, aes(x = modality, y = emmean, color = FS, group = FS)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +
  geom_errorbar(
    aes(ymin = lower.CL, ymax = upper.CL),
    width = 0.1,
    position = position_dodge(width = 0.3)
  ) +
  facet_wrap(~ LE, labeller = labeller(LE = c("off" = "Lesion Off", "on" = "Lesion On"))) +
  labs(
    x = "Structural modality",
    y = "Mean |E| (V/m)",
    color = "FreeSurfer"
  ) +
  theme_classic()
```


### d) Violin plot

```{r, echo=FALSE}

# Optional: precompute means per combination
means_df <- sub_data_all.df %>%
  dplyr::group_by(modality, FS, LE) %>%
  dplyr::summarise(mean_E = mean(p99_9, na.rm = TRUE), .groups = "drop_last")

LE_labels <- c(
  "t1" = "T1",
  "t1+t2" = "T1 + T2"
)

ggplot(sub_data_all.df,
       aes(x = LE,
           y = p99_9,
           fill = FS,
           color = FS)) +

  geom_violin(position = position_dodge(width = 0.7),
              alpha = 0.2,
              width = 0.7) +

  geom_jitter(position = position_jitterdodge(jitter.width = 0.15,
                                              dodge.width = 0.7),
              size = 1.5,
              alpha = 0.8) +

  geom_point(data = means_df,
             aes(x = LE, y = mean_E, fill = FS),
             shape = 23,
             size = 2.8,
             color = "black",
             position = position_dodge(width = 0.7)) +

  facet_wrap(~ modality, labeller = labeller(modality = LE_labels)) +
  scale_x_discrete(labels = c(
  "on" = "LE yes",
  "off" = "LE no"
)) +
  
    scale_fill_discrete(
    name = "FS",
    labels = c("off" = "no", "on" = "yes")
  ) +

  labs(x = "",
       y = "Peak e-field (V/m)",
       fill = "Freesurfer") +
  
  guides(color = "none") +   # remove duplicate legend

  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        strip.text = element_text(size = 11, face = "bold"),
        strip.background = element_blank(),
        #legend.position = c(0.98, 0.98),
        legend.position = 'none',
        legend.direction = "horizontal",
        legend.justification = c(1, 1),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 10))


# Save figure
ggsave("violin_99.9.png",
       dpi = 300,
       width = 5.5,
       height = 4,
       units = "in")


```


# 3 - Normal component

### a) Linear mixed-effect model

Results: Statistically significant differences for Freesurfer and lesion

```{r}
mod3 <- lmer(avg_roi_E_normal ~
               #Fixed Effects
               modality*FS*LE +
               #Random Effects
               (1|subID),
               #Define the data:
               data=sub_data_all.df, REML = TRUE)

summary(mod3)
```

### b) Stats report

```{r}

report(mod3)

```

### c) Marginal means

```{r, echo=FALSE}

# Get estimated marginal means for all 3 factors
emm_main <- emmeans(mod3, ~ modality * FS * LE)
emm_df   <- as.data.frame(emm_main)

# Plot with FS as color and LE as dodge (side-by-side)
ggplot(emm_df, aes(x = modality, y = emmean, color = FS, group = FS)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +
  geom_errorbar(
    aes(ymin = lower.CL, ymax = upper.CL),
    width = 0.1,
    position = position_dodge(width = 0.3)
  ) +
  facet_wrap(~ LE, labeller = labeller(LE = c("off" = "Lesion Off", "on" = "Lesion On"))) +
  labs(
    x = "Structural modality",
    y = "Mean |E| (V/m)",
    color = "FreeSurfer"
  ) +
  theme_classic()

```

### d) Violin plot

```{r, echo=FALSE}

# Optional: precompute means per combination
means_df <- sub_data_all.df %>%
  dplyr::group_by(modality, FS, LE) %>%
  dplyr::summarise(mean_E = mean(avg_roi_E_normal, na.rm = TRUE), .groups = "drop_last")

LE_labels <- c(
  "t1" = "T1",
  "t1+t2" = "T1 + T2"
)

ggplot(sub_data_all.df,
       aes(x = LE,
           y = avg_roi_E_normal,
           fill = FS,
           color = FS)) +

  geom_violin(position = position_dodge(width = 0.7),
              alpha = 0.2,
              width = 0.7) +

  geom_jitter(position = position_jitterdodge(jitter.width = 0.15,
                                              dodge.width = 0.7),
              size = 1.5,
              alpha = 0.8) +

  geom_point(data = means_df,
             aes(x = LE, y = mean_E, fill = FS),
             shape = 23,
             size = 2.8,
             color = "black",
             position = position_dodge(width = 0.7)) +

  facet_wrap(~ modality, labeller = labeller(modality = LE_labels)) +
  scale_x_discrete(labels = c(
  "on" = "LE On",
  "off" = "LE Off"
)) +
  
    scale_fill_discrete(
    name = "FS",
    labels = c("off" = "Off", "on" = "On")
  ) +
#scale_y_continuous(limits = c(-0.05, 0.18))+
  labs(x = "",
       y = "Normal component (V/m)",
       fill = "Freesurfer") +
  
  guides(color = "none") +   # remove duplicate legend

  theme_bw() +
  theme(axis.text.x = element_text(size = 11),
        strip.text = element_text(size = 11, face = "bold"),
        strip.background = element_blank(),
        #legend.position = c(0.98, 0.98),
        legend.position = 'none',
        legend.direction = "horizontal",
        legend.justification = c(1, 1),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 10))


# Save figure
ggsave("violin_normal.png",
       dpi = 300,
       width = 5.5,
       height = 4,
       units = "in")


```


